\section{Structure}

\begin{enumerate}
    \item \textbf{Introduction} \textit{(3 pages)}
    
    What is the motivation behind this thesis? What is the relevance of this thesis? What problem does this thesis try to solve? What kind of approach does this thesis take to solve that problem? How is the thesis structured?
    
    \item \textbf{Background} \textit{(6 pages)}
    
    What background knowledge is required to understand this thesis?
    \begin{enumerate}
        \item Neural Architecture Search (2.5 pages) 

        What is NAS used for, and how does it work? What is a NAS method? What are the origins of NAS? What environment are NAS methods typically developed in?

        \item Federated Learning (2.5 pages) 

        What is Federated Learning? What was it designed for and how does it work?

        \item Federated Neural Architecture Search (1 page) 
        
        How do FedNAS methods relate to NAS and FL? What are the origins of FedNAS methods, and how have they been developed over the last couple of years?
    \end{enumerate}
    
    \item \textbf{Method} \textit{(5 pages)}

    How does this thesis aim to achieve the objectives described in \autoref{sec:objectives}?
    \begin{enumerate}
        \item Reviewed Literature \textit{(2 pages)} Will include visualisations that break down the included literature for the reader.

        Which literature is included in the review?

        \item Methodology \textit{(3 pages)}

        How is the literature analysed? Which methodology is employed and how?
    \end{enumerate}

    \item \textbf{Challenges with Adapting Centralised NAS methods to FL} (10 pages): 
    \begin{enumerate}

        \item Assumption Discrepancies between NAS and FedNAS \textit{(3 pages)}
        
        How do centralised NAS and FedNAS differ? How does this difference manifest in different assumptions?

        \item Adaptation Challenges \textit{(4 pages)}
        
        How do FL system characteristics influence challenges faced in adapting centralised NAS methods to FL?

        \item Influence of FL system characteristics on Challenges \textit{(3 pages)}
        
        Which FL system characteristics influence the degree to which a challenge is relevant? Which FL system characteristics are relevant and which ones are not?
    \end{enumerate}
    
	\item \textbf{Adaptation Techniques} \textit{(25 pages)} 
    
    What adaptation techniques are described in the literature? What can we learn from these adaptation techniques that we can use for adapting NAS methods to FL in the future? For which FL system characteristics was each adaptation technique developed? How do adaptation techniques work towards, against, or do not affect overcoming each of the challenges relevant to that FL system characteristics?

    \begin{enumerate}
        \item Adaptation Technique 1 \textit{(1 page)} 
        
        Description of the refined adaptation technique, the FedNAS methods that use it and a discussion on how it overcomes challenges.
        \item Adaptation Technique 2 \textit{(1 page)}
        \item ...
        \item Adaptation Technique 20 \textit{(1 page)}
        \item Overview \textit{(5 pages)} A large overview table that makes it easy to see which adaptation techniques are beneficial for overcoming which challenges at a glance.
    \end{enumerate}

    \item \textbf{Discussion} \textit{(2 pages)}

    What do our findings indicate for the future of adapting centralised NAS methods to FL? How can researchers and practitioners use these contributions when adapting centralised NAS methods to targeted FL system characteristics?

    \item \textbf{Conclusion} \textit{(1 page)}
	
    What is the answer to the thesis's research question, and what are the main contributions? 
	
\end{enumerate}

\textit{52 pages} in total.